---
title: "Ramirez, Washington Co Jail, April 1"
output: html_document
---
## Install Packages

install.packages("rio")
install.packages("janitor")
install.packages("tidyverse")
install.packages("rmarkdown")
library("knitr")
knit2html("file")

## Data

```{r load data}
Roster_March18 <- rio::import("C://Users//Owner//Desktop//Spring 2020//WashCoInmates_3_27_2020.R.xlsx", which = "March18Roster")

Roster_March27 <- rio::import("C://Users//Owner//Desktop//Spring 2020//WashCoInmates_3_27_2020.R.xlsx", which = "March27Roster")

```

## Cleaning Data

```{r include=FALSE}
Roster_March18$name2 <- gsub(",","_", Roster_March18$`Name Last, First`)
Roster_March18$name2 <- gsub("\\s", "", Roster_March18$name2)

Roster_March27$name2 <- gsub(",","_", Roster_March27$`Name Last, First`)
Roster_March27$name2 <- gsub("\\s", "", Roster_March27$name2)

janitor::clean_names(Roster_March18)
janitor::clean_names(Roster_March27)
```

## Comparing Data

```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```

```{r setup}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
ReleasedInmates <-  Roster_March18 %>%
  anti_join(Roster_March27, by= "name2")

YAY <- Roster_March27 %>%
  inner_join(Roster_March18, by="name2")
```
## Q1: What is the difference between the two populations?

March 27 data had 637 inmates compared to the March 18 data that had 418 inmates. The "CompareTable" has 238 of the same inmates. 

## Q2: How many of the March 18 inmates were no longer listed as of March 27?

There were 180 inmates who were no longer listed on the March 27 roster from the March 18 roster.

## Q3: How many new inmates were there on March 27 that were not there on March 18?

On March 27, the Washington County jail had 218 new inmates compared to March 18.

## Q4: Describe percentage change of homeless people from March 18 to March 27.
On March 18, 73 of the 637 Washington County inmates were homeless, or 11% of the jailed population.

On March 27, 42 of the 418 Washington County inmates were homeless, or 10% of the jailed population.

Between March 18 and the 27, the Washington County had a 1.4% change of the jailed homeless population. 
```{r}
Roster_March18 %>%
  count(Homeless)

Roster_March27 %>%
  count(Homeless)

CompareTable %>%
  count(Homeless)